Self Regulation Ontology Retest Analyses

### 2018-10-16 code/SRO_Retest_Analyses.Rmd
refactoring and debugging

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))

ggsave('LitAndEmpAveCor.tiff', device = "tiff", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 7, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

```{r echo=FALSE}
rm(tmp, rel_comp, mod1, mod2, mod3, n_df, i, lit_emp_cor, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
```

@@

Based on [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) ICC(3,k) does not take in to account within subject differences between two time points (i.e. the fixed effect of time/systematic error). Thus, it is well approximated by Pearson's r and subject to similar criticisms. [Weir (2005)](https://pdfs.semanticscholar.org/d99a/790cce43f7f20d742f9d379b79de4f767740.pdf) suggests reporting at least this systematic error effect size if one chooses to report with ICC(3,k). Based on his conclusions here I report:  
- ICC(3,k): As Dave clarified this ranges from 1 to -1/(number of repeated measures -1) so in our case this range would be [-1, 1]; larger values would mean that the two scores of a subject for a given measure are more similar to each other than they are to scores of other people  
- "ICC is reflective of the ability of a test to differentiate between different individuals"
- partial $\eta^2$ for time ($SS_{time}/SS_{within}$): effect size of time   
- SEM ($\sqrt(MS_{error})$): standard error of measurement; the smaller the better. It
"quantifies the precision of individual scores on a test" and is not dependent on the sample in the way ICC is since it doesn't depend on between subject reliability (at least in this formulation) but is unit-dependent.

@@

```{r}
numeric_cols = c()

>>>>

```{r}
rel_comp %>%
  group_by(dv, task) %>%
  summarise(mean_lit = mean(retest_reliability),
            mean_emp = unique(mean_pearson)) %>%
  ggplot(aes(mean_emp, mean_lit, col=task, shape=task))+
  geom_smooth(method="lm")+
  geom_point()+
  xlim(-0.25, 1)+
  ylim(-0.25, 1)+
  ylab("Average Literature Reliability Estimate")+
  xlab("Average Empirical Reliability Estimate")+
  theme(legend.title = element_blank(),
        legend.position = 'bottom',
        plot.caption = element_text(family = "Times", lineheight = 2, hjust = 0))+
  labs(caption = str_wrap("FIGURE 2: Correlation between mean reliability estimates for each measure found in the literature with the mean reliability from our data.", width = 120))
```

```{r echo=FALSE}
rm(tmp, rel_comp, mod1, mod2, mod3, i, lit_emp_cor_out, comp_lit_pred, comp_lit_pred_out)
```

@@

@@

```{r}
rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))

numeric_cols = c()
